---
title: "RWorksheet_Pastor#4"
author: "Vincent Pastor"
date: "2022-11-21"
output: pdf_document
---

## RWorksheet #4

\hfill\break
1. The table below shows the data about shoe size and height. Create a data frame.

```{r, vector = TRUE}
Shoesize <- c(6.5,9.0,8.5,8.5,10.5,7.0,9.5,9.0,13.0,7.5,10.5,8.5,12.0,10.5)
Height <- c(66.0,68.0,64.5,65.0,70.0,64.0,70.0,71.0,72.0,64.0,74.5,67.0,71.0,71.0)
Gender <- c("F","F","F","F","M","F","F","F","M","F","M","F","M","M")
Shoe_size <- c(13.0,11.5,8.5,5.0,10.0,6.5,7.5,8.5,10.5,8.5,10.5,11.0,9.0,13.0)
Height_ <- c(77.0,72.0,59.0,62.0,72.0,66.0,64.0,67.0,73.0,69.0,72.0,70.0,69.0,70.0)
Gender_ <- c("M","M","F","F","M","F","F","M","M","F","M","M","M","M")

dframe <- data.frame(Shoesize, Height, Gender, Shoe_size, Height_, Gender_)
dframe


# a. Describe the data. - The data shows the different shoe size among male and female in different heights.
```

b. Find the mean of shoe size and height of the respondents. Copy the codes and results.

```{r, vector = TRUE}
mean1 <- mean(Shoesize)
mean1

mean2 <- mean(Shoe_size)
mean2

result1 <- c(mean1, mean2)
result1

# Total shoe size mean.
shoemean <- mean(result1)
shoemean

mean3 <- mean(Height)
mean3

mean4 <- mean(Height_)
mean4

result2 <- c(mean3, mean4)
result2

# Total height mean.
heightmean <- mean(result2)
heightmean
```

c. Is there a relationship between shoe size and height? Why? - 

```{r, vector = TRUE}
gtm <- mean(c(shoemean, heightmean))
gtm
```

Yes, there is a relationship between shoe size and height, the shoe sizes is big when the respondents is also tall. If the height of the respondents is below 70.0 their shoe size will be small.


## FACTORS

\hfill\break
2.Construct character vector months to a factor with factor() and assign the result to factor_months_vector. Print out factor_months_vector and assert that R prints out the factor levels below the actual values.Consider data consisting of the names of months:

```{r, vector = TRUE}
months_vector <- c("March","April","January","November","January","September","October","September","November","August","January","November","November","February","May","August","July","December","August","August","September","November","February","April")

factor_months_vector <- factor(months_vector)
factor_months_vector
```

\hfill\break
3. Then check the summary() of the months_vector and factor_months_vector. Interpret the results of both vectors. Are they both equally useful in this case?

```{r, vector = TRUE}
smry <- summary(months_vector)
smry

smry2 <- summary(factor_months_vector)
smry2
```

\hfill\break
4. Create a vector and factor for the table below.

```{r, vector = TRUE}
factor_data <- c("East" = '1', "West" = '4', "North" = '3')
factor_data

new_order_data <- factor(factor_data,levels = c("East" = '1',  "West" = '4',  "North" = '3'))
print(new_order_data)
```

\hfill\break
5. Enter the data below in Excel with file name = import_march.csv

a. Import the excel file into the Environment Pane using read.table() function. Write the code.

```{r, vector = TRUE}
import <- read.table("/cloud/project/RWorksheet_Pastor#4/import_march.csv", header = TRUE, sep= ",")
import
```

. View the dataset. Write the code and its result.
```{r, vector = TRUE}
view <- read.csv("/cloud/project/RWorksheet_Pastor#4/import_march.csv")
view

```
