---
title: 'RWorksheet #5'
author: "Vincent Pastor"
date: "2022-11-22"
output: pdf_document
---

## RWorksheet #5
\hfill\break
 1. The table shows the enrollment of BS in Computer Science, SY 2010-2011.

```{r, vector = TRUE}
stud <- data.frame("Course Year" = c ("1st", "2nd", "3rd", "4th"), " 2019–2020" = c(80, 75, 70, 60))
stud
```

 a. Plot the data using a bar graph. Write the codes and copy the result.

```{r, vector = TRUE}
a <- c("1st" = 80, "2nd" = 75, "3rd" = 70, "4th" = 60)
barplot(a)
```

 b. Using the same table, label the barchart with Title = ” Enrollment of BS Computer Science" horizontal axis = “Curriculum Year” and vertical axis = “number of students”

```{r, vector = TRUE}
a <- c("1st" = 80 , "2nd" = 75, "3rd" = 70, "4th" = 60)
barplot(a, main = "Enrollment of BS Computer Science", xlab = "number of students", ylab = "Course Year")
```

\hfill\break
 2. The monthly income of De Jesus family was spent on the following: 60% on Food, 10% on electricity, 5% for savings, and 25% for other miscellaneous expenses.

 a. Create a table for the above scenario. Write the codes and its result.

```{r, vector = TRUE}
sv <- c("Food", "Electricity", "Savings", "Miscellaneous_expenses")
mon <- c(60, 10, 5, 25)

spend <- data.frame(sv, mon)
spend

tab <- table(spend)
tab
```

 b. Plot the data using a pie chart. Add labels, colors and legend. Write the codes and its result.

```{r, vector = TRUE}
mon = c( 60, 10, 5, 25)

data <- round(mon/sum(mon)*100,1)
data <- paste(data, "%", sep = " ")

piechart <- pie( mon, labels = data, cex = 0.8, col = rainbow(4), main = "De Jesus family Monthly Expenses")
legend("topright", c("Food", "Electricity", "Savings", "Miscellaneous"),
       cex = 0.8 , fill =rainbow(4))
```

\hfill\break         
 3. Open the mtcars dataset.
 a. Create a simple histogram specifically for mpg (miles per gallon) variable. Use $ to select the mpg only. Write the codes and its result.

```{r, vector = TRUE}
data(mtcars)

mt <- (mtcars$mpg)
mt
        
hist(mtcars$mpg)
```

 b. Colored histogram with different number of bins. hist(mtcars$mpg, breaks=12, col="red") Note: breaks= controls the number of bins.

```{r, vector = TRUE}
hist(mtcars$mpg, breaks=12, col="red")
```

 c. Add a Normal Curve x <- mtcars$mpg h<-hist(x, breaks=10, col="red", xlab="Miles Per Gallon", main="Histogram with Normal Curve") xfit<-seq(min(x),max(x),length=40) yfit<-dnorm(xfit,mean=mean(x),sd=sd(x)) yfit <- yfit*diff(h$mids[1:2])*length(x) lines(xfit, yfit, col="blue", lwd=2) Copy the result.

```{r, vector = TRUE}
x <- mtcars$mpg

h<-hist(x, breaks=10, col="red", xlab="Miles Per Gallon",
        
        main="Histogram with Normal Curve")
xfit<-seq(min(x),max(x),length=40)
yfit<-dnorm(xfit,mean=mean(x),sd=sd(x))
yfit <- yfit*diff(h$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)
```

\hfill\break
 4. Open the iris dataset. Create a subset for each species.
 a. Write the codes and its result.

```{r, vector = TRUE}
data(iris)

allspcs <- data.frame(iris)
allspcs

setosaDF <- data.frame(iris)
setosaDF

virginicaDF <- data.frame(iris)
virginicaDF

versicolorDF <- data.frame(iris)
versicolorDF

setosa <- subset(setosaDF, Species == 'setosa' )
setosa

versicolor <- subset(versicolorDF, Species == 'versicolor' )
versicolor

virginica <- subset(virginicaDF, Species == 'virginica' )
virginica
```

 b. Get the mean for every characteristics of each species using colMeans(). Write the codes and its result. Example: setosa <- colMeans(setosa[sapply(setosaDF,is.numeric)])

```{r, vector = TRUE}
setosa1 <- colMeans(setosa[sapply(setosaDF,is.numeric)])
setosa1

virginica1 <- colMeans(virginica[sapply(virginicaDF,is.numeric)])
virginica1

versicolor1 <- colMeans(versicolor[sapply(versicolorDF,is.numeric)])
versicolor1
```

 c. Combine all species by using rbind() The table should be look like this:

```{r, vector = TRUE}
comb <- rbind( setosa1, versicolor1, virginica1)
dfiris <- data.frame(comb)
dfiris
```

 d. From the data in 4-c: Create the barplot(). Write the codes and its result. The barplot should be like this.

```{r, vector = TRUE}
barplot(height = as.matrix(dfiris),main = "Iris Data",
         ylab = "Mean Scores", 
         beside =T, col = rainbow(3)
        )
```


