---
title: "RWorksheet_Pastor#6"
author: "Vincent Pastor"
date: "2022-11-25"
output: pdf_document
---


1. How many columns are in mpg dataset? How about the number of rows? Show the codes and its result.
### - It has 11 columns and 234 rows.
```{r, include=TRUE}
library(dplyr)
library(ggplot2)

data(mpg)
data2 <- as.data.frame(mpg)
nrow(mpg)
ncol(mpg)
```

2. Which manufacturer has the most models in this data set? Which model has the most variations?
### - The manufacturer that has most model are the Dodge while the most variations of model are the caravan2wd.  
 
```{r, include=TRUE} 
mostmod <- data2 %>% group_by(manufacturer, model) %>%
  count()
mostmod

colnames(mostmod) <- c("Manufacturer","Model","Counts")
```

a. Group the manufacturers and find the unique models. Copy the codes and 
result.


```{r, include=TRUE}
uniquemods <- data2 %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
uniquemods

colnames(uniquemods) <- c("Manufacturer", "Model","Counts")
```

b. Graph the result by using plot() and ggplot(). Write the codes and its 
result.

```{r, include=TRUE}
plot(mostmod)
```

```{r, include=TRUE}
ggplot(mostmod, aes(Model, Manufacturer)) + geom_point()
```

3. Same dataset will be used. You are going to show the relationship of the 
model and the manufacturer.


```{r, include=TRUE}
mpgdata <- mpg
mod_fact <- data2 %>% group_by(manufacturer, model) %>%
  distinct() %>% count()
mod_fact

colnames(mod_fact) <- c("Manufacturer", "Model")
mod_fact
```

a. What does ggplot(mpg, aes(model, manufacturer)) + geom_point() show?

ggplot(mpg, aes(model, manufacturer)) + geom_point()
### - It shows the geometric point graph of mpg(model and manufacturer).

b. For you, is it useful? If not, how could you modify the data to make it 
more informative?

### -

4. Using the pipe (%>%), group the model and get the number of cars per model. 
Show codes and its result.

```{r, include=TRUE}
mpgdat <- data2 %>% group_by(model) %>% count()
mpgdat

colnames(mpgdat) <- c("Model","Counts")
mpgdat
```

a. Plot using the geom_bar() + coord_flip() just like what is shown below. 
Show codes and its result.

```{r, include=TRUE}
qplot(model,data = mpg,main = "Number of Cars per Model", xlab = "Model",
      ylab = "Number of Cars", geom = "bar", fill = manufacturer) +
  coord_flip()
```

#b. Use only the top 20 observations. Show code and results.

```{r, include=TRUE}
mpg2 <- mpgdat[1:20,] %>% top_n(2)
mpg2

ggplot(mpg2, aes(x = Model, y = Counts)) + 
  geom_bar(stat = "identity") + coord_flip()
```

5. Plot the relationship between cyl - number of cylinders and displ - 
engine displacement using geom_point with aesthetic colour = engine 
displacement. Title should be
“Relationship between No. of Cylinders and Engine Displacement”.

a. Show the codes and its result.

```{r, include=TRUE}
ggplot(data = mpg , mapping = aes(x = displ, y = cyl, main = "Relationship 
                                    between No of Cylinders and 
                                    Engine Displacement")) + 
  geom_point(mapping=aes(colour = "engine displacement")) 
```

b. How would you describe its relationship?

### - The scatter plot shows that the "cyl" is a number of cylinders in y and the "displ" is an engine displacement x.

6. Get the total number of observations for drv - type of drive train 
(f = front-wheel drive,
r = rear wheel drive, 4 = 4wd) and class - type of class (Example: suv, 
2seater, etc.).

Plot using the geom_tile() where the number of observations for class be 
used as a fill for aesthetics.

a. Show the codes and its result for the narrative in #6.

```{r, include=TRUE}
ggplot(data = mpg, mapping = aes(x = drv, y = class)) +
  geom_tile(aes(fill=class))
```

b. Interpret the result.

### - By adding color to the geom_tile you can see the different type of drive train and the class.


7. Discuss the difference between these codes. Its outputs for each are shown below.


8. Try to run the command ?mpg. What is the result of this command?

```{r, include=TRUE}
?mpg

```
### - The result are directed you to help option showing the data mpg.

a. Which variables from mpg dataset are categorical?

### - The manufacturer trans ,model, drv, fl, class
are the categorical variables from the data-set of mpg.

b. Which are continuous variables?

### - The continuous variable of the mpg data-set are the dsipl, cyl etc.

c. Plot the relationship between displ (engine displacement) and hwy(highway 
miles per gallon). Mapped it with a continuous variable you have identified 
in #5-b. What is its result? Why it produced such output?

```{r, include=TRUE}
ggplot(mpg, aes(x = displ, y = hwy, colour = cty)) + geom_point()
```
### - The data shows that they are in the positive rate using the displ for hwy and cty scattered plot.

9. Plot the relationship between displ (engine displacement) and hwy(highway
miles per gallon) using geom_point(). Add a trend line over the existing plot 
using geom_smooth() with se = FALSE. Default method is “loess”.

```{r, include=TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy)) +
  geom_point(mapping=aes(color=class)) +
  geom_smooth(se = FALSE)
```

10. Using the relationship of displ and hwy, add a trend line over existing 
plot. Set these = FALSE to remove the confidence interval and method = lm to 
check for linear modeling.

```{r, include=TRUE}
ggplot(data = mpg, mapping = aes(x = displ, y = hwy, color = class)) +
  geom_point() +
  geom_smooth(se = FALSE, method = lm)
```
